\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-03-30 paper.tex
Added updated notation.csv

\caption{\label{tab:tbl-notations}Notations used in this paper.}
\centering
\begin{tabular}[t]{ll}
\toprule
\textbf{Notation} & \textbf{Description}\\
\midrule
$n$ & number of observations\\
$p$ & number of dimensions in $p-D$ data\\
$X_{n \times p} = \begin{bmatrix} \textbf{x} _{1} & \textbf{x}_ {2} & \cdots & \textbf{x}_{n} \\  \end{bmatrix}^\top$ & $p-D$ data matrix\\
$d$ & number of dimensions in embedding data, usually two\\
$Y_{n \times d} = \begin{bmatrix} \textbf{y} _{1} & \textbf{y}_ {2} & \cdots & \textbf{y}_{n} \\  \end{bmatrix}^\top$ & embedding matrix\\
\addlinespace
$P_t$ & point along the geodesic path at time $t$\\
$P_{t+1}$ & point along the geodesic path at the next time instant, which is $t+1$\\
$y_max$ & maximum value of the scaled second embedding component\\
$r_1$ & range of the first embedding component\\
$r_2$ & range of the second embedding component\\
\addlinespace
$h_b$ & height of the hexagon\\
$w_b$ & width of the hexagon\\
$a_r$ & aspect ratio of the 2D layout before scaling\\
$h_r$ & hexagon ratio\\
$s$ & hexagonal size (radius of the outer circle surrounding the hexagon)\\
\addlinespace
$(x_s, y_s)$ & starting coordinates of the hexagonal grid\\
$q_x$ & buffer amount along the x-axis\\
$q_y$ & buffer amount along the y-axis\\
$h_s$ & horizontal distance between
adjacent hexagon bin \vphantom{1} centroids\\
$v_s$ & vertical distance between
adjacent hexagon bin centroids\\
\addlinespace
$d_x$ & horizontal spacing\\
$d_y$ & adjusted vertical spacing for hexagonal coordinates\\
$b_x$ & number of hexagon bins along the x-axis\\
$b_y$ & number of hexagon bins along the y-axis\\
$b$ & total number of hexagon bins in the grid\\
\addlinespace
$b'$ & number of hexagon bins without the empty bins\\
$n_k$ & number of observations within $k^{th}$ hexagon\\
$(h^k_{x_i}, h^k_{y_i})$ & hexagonal grid coordinates of $k^{th}$ hexagon\\
$C_k^{(2)} \equiv (C_{ky_1}, C_{ky_2})$ & hexagonal bin centroid coordinates of $k^{th}$ hexagon\\
$C_k^{(p)} \equiv (C_{kx_1}, ..., C_{kx_p})$ & $p-D$ mappings of 2D hexagonal bin centroids of $k^{th}$ hexagon\\
\bottomrule
\end{tabular}
\end{table}

>>>>

\caption{\label{tab:tbl-notations}Notations used in this paper.}
\centering
\begin{tabular}[t]{ll}
\toprule
\textbf{Notation} & \textbf{Description}\\
\midrule
$n$ & number of observations\\
$p$ & number of dimensions in high-D data\\
$X_{n \times p} = \begin{bmatrix} \textbf{x} _{1} & \textbf{x}_ {2} & \cdots & \textbf{x}_{n} \\  \end{bmatrix}^\top$ & high-D data matrix\\
$d$ & number of dimensions in embedding data, usually two\\
$Y_{n \times d} = \begin{bmatrix} \textbf{y} _{1} & \textbf{y}_ {2} & \cdots & \textbf{y}_{n} \\  \end{bmatrix}^\top$ & embedding matrix\\
\addlinespace
$P_t$, $P_{t+1}$ & point along the geodesic path at time $t$ and the next time instant, which is $t+1$\\
$y_max$ & maximum value of the scaled second embedding component\\
$r_1$, $r_2$ & range of the first and  second embedding component\\
$h_b$, $w_b$ & height and width of the hexagon\\
$a_r$ & aspect ratio of the 2D layout before scaling\\
\addlinespace
$h_r$ & hexagon ratio\\
$s$ & hexagonal size (radius of the outer circle surrounding the hexagon)\\
$(x_s, y_s)$ & starting coordinates of the hexagonal grid\\
$q_x$, $q_y$ & buffer amount along the x and y axes\\
$h_s$, $v_s$ & horizontal and vertical distance between adjacent hexagon bin centroids\\
\addlinespace
$d_x$ & horizontal spacing\\
$d_y$ & adjusted vertical spacing for hexagonal coordinates\\
$b_x$, $b_y$ & number of hexagon bins along the x and y axes\\
$b$ & total number of hexagon bins in the grid\\
$b'$ & number of hexagon bins without the empty bins\\
\addlinespace
$n_k$ & number of observations within $k^{th}$ hexagon\\
$(h^k_{x_i}, h^k_{y_i})$ & hexagonal grid coordinates of $k^{th}$ hexagon\\
$C_k^{(2)} \equiv (C_{ky_1}, C_{ky_2})$ & hexagonal bin centroid coordinates of $k^{th}$ hexagon\\
$C_k^{(p)} \equiv (C_{kx_1}, ..., C_{kx_p})$ & high-D mappings of 2D hexagonal bin centroids of $k^{th}$ hexagon\\
\bottomrule
\end{tabular}
\end{table}
